Embedding Dimension of Polyhedral Losses

### 2020-01-31 colt-20/embed-dim.tex
Pass over intro.  Just changing the embedding notation

The question therefore becomes: Given a discrete loss $\ell$, how do we design such calibrated surrogates $L$? 
The class of surrogates studied in this paper are \emph{polyhedral}, meaning piece-wise linear convex functions over prediction space $\reals^d$.
\cite{finocchiaro2019embedding} show that polyhedral surrogates are equivalent to the following recipe: \emph{embedding} the discrete loss $\ell$ into $\reals^d$ by letting each discrete prediction $r$ correspond to some point $\phi(r) \in \reals^d$, which optimizes $L$-loss if and only if $r$ optimizes $\ell$-loss.
\cite{finocchiaro2019embedding} show that every discrete loss $\ell$ can be embedded into \emph{some} dimension $d$.
But in the worst case $d=n-1$ where $n$ is the number of possible observations $y$, e.g. a number of classification categories.

>>>>

The question therefore becomes: Given a discrete loss $\ell$, how do we design such calibrated surrogates $L$? 
The class of surrogates studied in this paper are \emph{polyhedral}, meaning piece-wise linear convex functions over prediction space $\reals^d$.
\cite{finocchiaro2019embedding} show that polyhedral surrogates are equivalent to the following recipe: \emph{embedding} the discrete loss $\ell$ into $\reals^d$ by letting each discrete prediction $r$ correspond to some point $\varphi(r) \in \reals^d$, which optimizes $L$-loss if and only if $r$ optimizes $\ell$-loss.
\cite{finocchiaro2019embedding} show that every discrete loss $\ell$ can be embedded into \emph{some} dimension $d$.
But in the worst case $d=n-1$ where $n$ is the number of possible observations $y$, e.g. a number of classification categories.
